Studying the Performance of the Jellyfish Search Optimiser for the Application of Projection Pursuit

### 2024-06-26 optim.qmd
bullet point conclusions

The data structure proposed in @RJ-2021-105 is implemented for JSO. 
An example data collected from finding the sine-wave structure
in 6D data using a spline index function (`splines2d`) is
printed below:

@@

>>>>

The data structure proposed in @RJ-2021-105 is used here for assessing JSO. A sample for the sine-wave structure in 6D data using a spline index function (`splines2d`) is printed below:

@@

- Summarise the result of the simulation: JSO immense improvement on current methods, ...
- JSO for a guided tour, what changes are needed? Do we follow one tentacle, do we perform off-line and then pull tentacles out to watch, how does it integrate with ferrn

### 2024-06-26 optim.tex
bullet point conclusions

\begin{tcolorbox}[enhanced jigsaw, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toprule=.15mm, toptitle=1mm, bottomrule=.15mm, breakable, colback=white, colframe=quarto-callout-note-color-frame, leftrule=.75mm, coltitle=black, opacitybacktitle=0.6, title={Algorithm: Jellyfish Optimizer Pseudo Code}, arc=.35mm, titlerule=0mm, left=2mm, opacityback=0, rightrule=.15mm]

@@

The data structure proposed in \citet{RJ-2021-105} is implemented for
JSO. An example data collected from finding the sine-wave structure in
6D data using a spline index function (\texttt{splines2d}) is printed
below:

@@

>>>>

\begin{tcolorbox}[enhanced jigsaw, colback=white, toprule=.15mm, titlerule=0mm, colbacktitle=quarto-callout-note-color!10!white, rightrule=.15mm, toptitle=1mm, coltitle=black, leftrule=.75mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, opacityback=0, breakable, colframe=quarto-callout-note-color-frame, opacitybacktitle=0.6, left=2mm, bottomtitle=1mm, arc=.35mm, bottomrule=.15mm]

@@

The data structure proposed in \citet{RJ-2021-105} is used here for
assessing JSO. A sample for the sine-wave structure in 6D data using a
spline index function (\texttt{splines2d}) is printed below:

@@

\begin{itemize}
\tightlist
\item
  Summarise the result of the simulation: JSO immense improvement on
  current methods, \ldots{}
\item
  JSO for a guided tour, what changes are needed? Do we follow one
  tentacle, do we perform off-line and then pull tentacles out to watch,
  how does it integrate with ferrn
\end{itemize}
